### 2020-07-10 nb/analysis_in_R.Rmd
start making LeagueResults function

@@

```{r}
sort(ExpectedScoringTime(
    TransitionMatrix(
        GameGraph(events, match_id, home_or_away='Away'))

))
```

>>>>

```{r}
LeagueResults <- function(league){

    teams <- sort(unique(league$team))

    home_score <- matrix(0, nrow=20, ncol=20)
    colnames(home_score) <- teams
    rownames(home_score) <- teams

    away_score <- home_score

    league_table <- matrix(0, nrow=20, ncol=8)
    rownames(league_table) <- teams
    colnames(league_table) <- c('POS','PTS','W','D','L','GF','GA','GD')

    return(list(league_table, home_score, away_score))
}
```

```{r}
v <- LeagueResults(events)
```

```{r}
hs <- v[[2]]
```

```{r}
league <- events
```

```{r}
teams <- sort(unique(league$team))

home_score <- matrix(0, nrow=20, ncol=20)
colnames(home_score) <- teams
rownames(home_score) <- teams

away_score <- home_score

league_table <- matrix(0, nrow=20, ncol=8)
rownames(league_table) <- teams
colnames(league_table) <- c('POS','PTS','W','D','L','GF','GA','GD')
```

```{r}
for m in unique(league$matchId){

    match <- league[league$matchId==m,]
    home_team <- unique(match[match$home_or_away=='Home']$team)
    away_team <- unique(match[match$home_or_away=='Away']$team)
    home_goals <- nrow(match[match$to_team=='Home Goal',])
    away_goals <- nrow(match[match$to_team=='Away Goal',])

    home_score[home_team, away_team] <- home_goals
    away_score[home_team, away_team] <- away_goals

    league_table[]

        league_table[team]
    }

```{r}
league_table
```

```{r}
for (match in unique(events$matchId)){

    goals <- 0

```{r}
mId <- unique(events$matchId)[1]
```

```{r}
m <- events[events$matchId==mId,]
```

```{r}
home_goals <- m[m$to_team=='Home Goal',]
```

```{r}
away_goals <- m[m$to_team=='Away Goal',]
```

```{r}
home_goals <- matrix(0, nrow=20, ncol=20)
```

```{r}
away_goals <- matrix(0, nrow=20, ncol=20)
```

```{r}
colnames(home_goals) <- teams
```

```{r}
rownames(home_goals) <- teams
```

```{r}
home
```

```{r}
home_goals
```

```{r}
teams <- sort(unique(events$team))
```

@@

```{r}
x_score_time <- ExpectedScoringTime(
    TransitionMatrix(
        GameGraph(events, match_id, home_or_away='Home'))

```{r}
x_score_time/mean(x_score_time)
```

```{r}
x_score_time/mean(x_score_time)
```
